Brundle Development

### 2017-11-28 Manuscript_Figures.Rmd
Updated Markdown

>>>>

## Changes in H4K12ac following E2 treatment

```{r,results='hide', message=FALSE, warning=FALSE}
filename<-"Rdata/066_SLX-15090_dba_human_ER_CTCF.rda"
load(filename)

#install_github("andrewholding/Brundle")
library(Brundle)

jg.controlSampleSheet     <- "samplesheet/samplesheet_SLX15090_CTCF.csv"
jg.experimentSampleSheet  <- "samplesheet/samplesheet_SLX15090_H4K12ac.csv"
jg.treatedCondition       =  "Estrogen"
jg.untreatedCondition     =  "none"

jg.dba<-Brundle(
            dbaExperiment,
            dbaControl,
            jg.treatedCondition,
            jg.untreatedCondition,
            jg.experimentSampleSheet,
            jg.controlSampleSheet )

jg.dba_analysis<-dba.analyze(jg.dba)
dba.plotMA(jg.dba_analysis,bFlip=TRUE,th=0.05)

```{r,results='hide', message=FALSE, warning=FALSE}

jg.plotPanelsPlot<-function(treatmentNames,controlNames,dbaExperiment,noYLabel=FALSE)
{

#Worse correlation is 2a-3a (control sample)
controlNames<-c("2a","3a")

jg.experimentPeakset <- jg.dbaGetPeakset(dbaExperiment)
relativeLibrarySize<-jg.getLibrarySize(dbaExperiment,
                                       jg.experimentPeakset)
peaksLibrarySize<-relativeLibrarySize[controlNames]
peaks<-jg.experimentPeakset[controlNames]
peaks[1]<-round(peaks[1]/peaksLibrarySize[1])
peaks[2]<-round(peaks[2]/peaksLibrarySize[2])
x<-c("Rep2","Rep3")
names(x)<-controlNames
x<-as.matrix(x)
jg.plotScatter(peaks,controlNames, T,t(x),FALSE)
Axis(side=2, labels=TRUE,ylab="Log(Counts)")
mtext("log(Counts)", side=2, line=3)

```{r,results='hide', message=FALSE, warning=FALSE}

profile<-read.table("SLX-15090/Homer_Profile.txt",sep="\t")
profile_ER<-as.matrix(profile[,c(1,2)])
plot(profile_ER,t="l",col="red", xlab="Distance from TSS",ylab="Read Depth",main="H4K12ac Profile")
profile_Ctrl<-as.matrix(profile[,c(1,5)])
lines(profile_Ctrl,col="blue")
legend("topright",legend = c("Estrogen", "Control"), col=c("red","blue"),pch = c(19,19))
abline(v=0, lty=3)

## Activation of ER in MCF7

```{r,results='hide', message=FALSE, warning=FALSE}

jg.controlSampleSheet     <- "samplesheet/samplesheet_SLX15091_CTCF.csv"
jg.experimentSampleSheet  <- "samplesheet/samplesheet_SLX15091_ER.csv"
jg.treatedCondition       =  "Estrogen"
jg.untreatedCondition     =  "none"

#####
#
# Main Code
#
#####

filename<-"Rdata/065_SLX-15091_dba_human_ER_CTCF.rda"
load(filename)

jg.dba<-Brundle(
            dbaExperiment,
            dbaControl,
            jg.treatedCondition,
            jg.untreatedCondition,
            jg.experimentSampleSheet,
            jg.controlSampleSheet )

jg.dba_analysis<-dba.analyze(jg.dba)
dba.plotMA(jg.dba_analysis,bFlip=TRUE,th=0.05)

```{r,results='hide', message=FALSE, warning=FALSE}
#Check CTCF

controlNames<-c("1a","3b")

jg.experimentPeakset <- jg.dbaGetPeakset(dbaExperiment)
relativeLibrarySize<-jg.getLibrarySize(dbaExperiment,
                                       jg.experimentPeakset)
peaksLibrarySize<-relativeLibrarySize[controlNames]
peaks<-jg.experimentPeakset[controlNames]
peaks[1]<-round(peaks[1]/peaksLibrarySize[1])
peaks[2]<-round(peaks[2]/peaksLibrarySize[2])
x<-c("Rep1","Rep3")
names(x)<-controlNames
x<-as.matrix(x)
jg.plotScatter(peaks,controlNames, T,t(x),FALSE)
Axis(side=2, labels=TRUE,ylab="Log(Counts)")
mtext("log(Counts)", side=2, line=3)
